Xolotl: An Intuitive and Comprehensible Neuronal Simulator

### 2018-05-18 PaperLatex/frontiers.tex
minor fixes

\title[xolotl: the god of thunder]{Xolotl: A Fast and Comprehensible Neuronal Simulator}

@@

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{\texttt{xolotl} readily implements voltage clamp. (A) Cartoon of a cell with potassium conductance with experimentally-fixed voltage. (B) Structure of \texttt{xolotl} object in A. (C) Code snippet depicting integration under voltage clamp. (D-E) Current response to steps in voltage from a holding potential of $V_m = -60$ mV. (F) Current-voltage relation of the steady-state current ($t = 400$ ms) indicating a reversal potential of $E = -80$ mV and no inactivation. (G) Conductance-voltage relation at steady-state takes the form of a sigmoid. (H) Sigmoids of the form $m^n$ fit to the model data indicating that $n=4$ is the best fit. (I) $R^2$ correlation of the sigmoid fits at various powers where $n=4$ is an exact fit.}
	\label{fig:figureclamp}
\end{figure}

>>>>

\title[xolotl: neuronal simulator]{Xolotl: An Intuitive and Comprehensible Neuronal Simulator}

@@

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{\texttt{xolotl} readily implements voltage clamp. (A) Cartoon of a cell with potassium conductance with experimentally-fixed voltage. (B) Structure of \texttt{xolotl} object in A. (C) Code snippet depicting integration under voltage clamp. (D-E) Current response to steps in voltage from a holding potential of $V_m = -60$ mV. (F) Current-voltage relation of the steady-state current ($t = 400$ ms) indicating a reversal potential of $E = -80$ mV and no inactivation. (G) Conductance-voltage relation at steady-state takes the form of a sigmoid. (H) Sigmoids $m$ fit to the model as $m^n$ data indicating that $n=4$ is the best fit. (I) $R^2$ correlation of the sigmoid fits at various powers where $n=4$ is an exact fit.}
	\label{fig:figureclamp}
\end{figure}
